VM-Centric Snapshot Deduplication for Converged Cloud Architectures

### 2014-07-18 snapshot_system/concl.tex

\section{Conclusion}
\label{sect:final}
In this paper we propose a collocated backup service built on
the top of a cloud cluster to reduce network traffic and infrastructure.
The key contribution is a VM-centric deduplication scheme to 
maximize fault isolation while delivering competitive deduplication efficiency.
Inner-VM deduplication localizes backup data dependency and exposes more parallelism  
while cross-VM deduplication with a small common data set.
VM-specific file block packing also reduces inter-VM dependence and enhances fault tolerance.
The design places a special consideration for low-resource usages as a collocated cloud service.
Evaluation using  VM backup data shows that
our solution can accomplish 92\% of what complete global
deduplication can do while the availability of snapshots increases substantially with this VM-centric
and a small replication overhead for popular inter-VM chunks.

% effectively  covers a large percent of duplicate data.
%The scheme organizes the write of small data chunks into large file system blocks so
%that each underlying file block is associated with one VM for most cases.
%by keeping most of the FSBs only referenced by 1 VM, we isolate faults and improve overal fault tolerance.
%Our solution accomplishes reasonable and competitive deduplication efficiency while
%still meeting stringent cloud resource usage requirements. 
%Our analysis shows that  this VM centric scheme 
%can  provide  better fault tolerance than VM-oblivious global deduplication schemes
%while using a small amount of computing and storage resources.

>>>>

\section{Conclusion}
\label{sect:final}
In this paper we propose a collocated backup service with source-side deduplication built on
the top of a cloud cluster to reduce network traffic and infrastructure cost.
The design places a special consideration for low-resource usages as a collocated cloud service.
The main contribution is a VM-centric deduplication scheme to play
a tradeoff for low resurce usages and competitive deduplication efficiency. 
%It also maximizes fault isolation by seperating popular and non-
Inner-VM deduplication with similarity-guided local search
maximizes the deduplication efficiency while
localizing backup data dependency and exposing more parallelism during deduplication.  
Cross-VM deduplication with a small popular data set leverages the zipf characteristics
of popular items. 
VM-specific file block packing reduces inter-VM dependence and enhances fault tolerance.

The evaluation based on  an  Alibaba  production dataset 
shows that our solution can accomplish 92\% of what complete global
deduplication can do while the availability of snapshots increases substantially with this VM-centric
and a small replication overhead for popular inter-VM chunks.

Comparing the experiment results of the sampled index method reported in~\cite{Guo2011},
our scheme achives a 86K:1 ratio between raw snapshot data and memory usage
with 96\% deduplication efficiency
while the sampled index method achives 20K:1 (10GB memory per 500TB raw data)
with 97\% deduplication efficiency.
Thus our scheme is more memory efficient with a good tradeoff for deduplication efficiency.
If we change $\sigma=4\%$, the deduplication efficiency of VC increases to 96.58\% while
memory usage per machine increses to about 220MB.
Notice that the sampled index method is designed for single-machine deduplication
and it is not easy to extend to a distributed cluster architecture.
% effectively  covers a large percent of duplicate data.
%The scheme organizes the write of small data chunks into large file system blocks so
%that each underlying file block is associated with one VM for most cases.
%by keeping most of the FSBs only referenced by 1 VM, we isolate faults and improve overal fault tolerance.
%Our solution accomplishes reasonable and competitive deduplication efficiency while
%still meeting stringent cloud resource usage requirements. 
%Our analysis shows that  this VM centric scheme 
%can  provide  better fault tolerance than VM-oblivious global deduplication schemes
%while using a small amount of computing and storage resources.

### 2014-07-18 snapshot_system/paper_eval.tex

Comparing the experiment results of the sampled index method reported in~\cite{Guo2011}, 
our scheme achives a 86K:1 ratio between raw snapshot data and memory usage 
with 96\% deduplication efficiency
while the sampled index method achives 20K:1 (10GB memory per 500TB raw data)
with 97\% deduplication efficiency.
Thus our scheme is more memory efficient with a good tradeoff for deduplication efficiency.
If we change $\sigma=4\%$, the deduplication efficiency of VC increases to 96.58\% while
memory usage per machine increses to about 220MB. 
Notice that the sampled index method is designed for single-machine deduplication
and it is not easy to extend to a distributed cluster architecture.

@@

 Table~\ref{tab:vm-availability} shows the availability of VM snapshots when 
there are up to 20 machines failed in a cluster. 
The trace driven execution allows us to estimate the number of file blocks shared by each VM in the VO and VC approaches
and then calculate the average availability of VM snapshots.
The case for  a 1000-node cluster is also listed, assuming file block sharing patterns among VMs remain
the same from $p=100$ setting to $p=1000$. Each machine hosts about 25 VMs in both cases
and with different $p$ values, the availability varies when the number of failures in the cluster changes.

>>>>

Comparing the experiment results of the sampled index method reported in~\cite{Guo2011}, 
our scheme achives a 85K:1 ratio between raw snapshot data and memory usage 
with 96\% deduplication efficiency
while the sampled index method achives 20K:1 (10GB memory per 500TB raw data)
with 97\% deduplication efficiency.
Thus our scheme is more memory efficient with a good tradeoff for deduplication efficiency.
If we change $\sigma=4\%$, the deduplication efficiency of VC increases to 96.58\% while
memory usage per machine increses to about 220MB. 
Notice that the sampled index method is designed for single-machine deduplication
and it is not easy to extend to a distributed cluster architecture.

@@

We demonstrate  the impact of adding extra replication for PDS in VC
and compare the snapshot availability of VC and VO. 
Appendix~\ref{sect:fault} provides a detailed analysis of 
snapshot availablility and the estimated result depends on how frequent a duplicate chunk
is shared among snapshots of VMs.
The trace driven execution allows us to estimate the number of file blocks shared by each VM in the VO 
and VC approaches
and then calculate the average availability of VM snapshots.

Table~\ref{tab:vm-availability} shows the estimated availability of VM snapshots when 
there are up to 20 machines failed in a cluster. 
The case for  a 1000-node cluster is also listed, assuming file block sharing patterns among VMs remain
the same from $p=100$ setting to $p=1000$. Each machine hosts about 25 VMs in both cases
and with different $p$ values, the availability varies when the number of failures in the cluster changes.
